---
title: "Travel insurance"
author: "Yuta Chen"
date: "6/3/2022"
output: html_document
---


```{r}
setwd("~/Desktop/HS 614 Clinical Decision Support ")
df<-read.csv('travel_insurance.csv')
head(df)
```

#Library
```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
#library(tidyverse)
#library(janitor)
library(readr)
```

#Summary
#Average age of the travalers are 29.65 years old
#Average annual income for the travalers are $932,763
#They travled with 4.753 family members 
#27.78% of the travelers with chronic disease 
```{r}
summary(df)
```

#Sructure
```{r}
str(df)
```


###EDA

#Age
```{r}
ggplot(data=df)+geom_density(aes(x=Age), color='black')+ 
  theme(axis.text = element_text(colour = "blue"),text = element_text(size=15),axis.line = element_line(size = 1, colour = "grey80"))+ggtitle(labs(title = 'Distribution of Age'))
```

#Distribution of travelers from different age group with travel insurance purchased
```{r}
ggplot(df, aes(Age)) + geom_bar(aes(fill=factor(TravelInsurance))) + ggtitle(labs(title = 'Age vs. Travel Insurance'))
```

#Boxplot shows us that travelers who bought insuarnce are about 20 years old, slightly older than the travellers without insuarnce
```{r}
ggplot(df,aes(x=TravelInsurance, y=Age, group=TravelInsurance, fill=TravelInsurance)) + geom_boxplot() + labs(y='Age')
```


#Employmeny Type
#Private sector/self employed travelers are about 2 times more than gevernment sector
```{r}
ggplot(df, aes(EmploymentType))+geom_bar(fill='bisque2',color='black') + ggtitle('Distribution of Employment Type')
```

#Travellers who work in government sector have insurances less than travellers who works in Private Sector/Self Employed
```{r}
ggplot(df, aes(EmploymentType)) + geom_bar(aes(fill=factor(TravelInsurance)), position='dodge') + ggtitle("Employment Type vs. Travel Insurance")
```



#Graduate or not 
#1692 graduate / 295 do not grauate 
```{r}
ggplot(df, aes(GraduateOrNot))+geom_bar(fill='gold3', color='black')+ ggtitle('Distribution of Graduation or Not')
table(df$GraduateOrNot)
```

#Graduate level is not a good factor to determine if a traveller will purchase the insuarce or not 
```{r}
ggplot(df, aes(GraduateOrNot)) + geom_bar(position='dodge',aes(fill=factor(TravelInsurance))) + ggtitle(labs('Graduate vs. Insuarance'))
```


#Annual Income 
```{r}
ggplot(df, aes(AnnualIncome))+geom_density(fill='red', alpha=0.4)+ ggtitle('Distribution of Annual Income')
```


#Higher annual income the traveler make, more likely the traveller with purchase travel insuarance 
```{r}
ggplot(df, aes(AnnualIncome)) + geom_density(aes(fill=factor(TravelInsurance)), alpha=0.5) + ggtitle("Annual Income vs. Insuarance")
```


#Family Members
```{r}
ggplot(df, aes(FamilyMembers))+geom_bar(fill='cyan3',color='black')+ ggtitle('Distribution of Family Members')

table(df$FamilyMembers)
```

#Density plot shows that there is no strong relationship between the number of family members and travel insuarance purchased
```{r}
ggplot(df, aes(FamilyMembers)) + geom_density(aes(fill=factor(TravelInsurance)), alpha=0.4) + ggtitle("Family Members vs. Insuarance")
```

#Boxplot shows that the average family memebers from both groups are the same, but insuranced family has more cases of having more 6 members
```{r}
ggplot(df, aes(FamilyMembers)) + geom_boxplot(aes(fill=factor(TravelInsurance))) + ggtitle("Family Members vs. Insuarance")
```


#Chronic Diseases
#Most of the travellers are without chronic diseases
```{r}
ggplot(df, aes(ChronicDiseases))+geom_bar(fill='azure2', color='black')+ ggtitle('Distribution of Chronic Diseases')

table(df$ChronicDiseases)
```

#The travelers who developed chronic diseases tends to have no travel insurance which might due to the insurace company declined their travel insurace because of theor health status
```{r}
ggplot(df, aes(ChronicDiseases)) + geom_bar(aes(fill=factor(TravelInsurance)), position='dodge') + ggtitle("Chronic disease vs. Travel Insurance")
```


#Frequent Flyer
```{r}
ggplot(df, aes(FrequentFlyer))+geom_bar(fill='pink', color='black') + ggtitle("Distribution of Frequent Flyer")
```

#Nearly half of the non-frequent-flyers have travel insuarnce, and there is more frequent-travelers with travel insuarance than those frequent-travelers without travel insuarance
```{r}
ggplot(df, aes(FrequentFlyer)) + geom_bar(aes(fill=factor(TravelInsurance)), position='dodge') + ggtitle("Frequent Flyer vs. Travel Insurance")
```

#Ever Travel Abroad
#The travellers never travel abroad are almost 4 times more than travellers who have traveled abroad before
```{r}
ggplot(df, aes(EverTravelledAbroad))+geom_bar(fill='violet', color='black') + ggtitle("Distribution of Ever Travel Abroad")
```

#Bar plot shows that the travallers with experience of travel abroad are more likely to purchase travel insuarance
```{r}
ggplot(df, aes(EverTravelledAbroad)) + geom_bar(aes(fill=factor(TravelInsurance)), position='dodge') + ggtitle("Ever Travelled Abroad vs. Travel Insurance")
```

###Summarize 
#Average age of the travalers are 29.65 years old
#Average annual income for the travalers are $932,763
#They travled with 4.753 family members 
#27.78% of the travelers with chronic disease 

###Build model predict with factors lead to travel insurace purchased

#Create dummy variable for Employment type with 0 and 1
```{r}
#df$EmploymentType <- ifelse(df$EmploymentType == "Government Sector",0,1)

#table(df$EmploymentType)
```

#Convert categoriacl variables into factors for model building 
```{r}
str(df)

df$EmploymentType<-as.factor(df$EmploymentType)
df$GraduateOrNot<-as.factor(df$GraduateOrNot)
df$FrequentFlyer<-as.factor(df$FrequentFlyer)
df$EverTravelledAbroad<-as.factor(df$FrequentFlyer)
df$TravelInsurance<-as.factor(df$TravelInsurance)
```



#Split data into train and test data set 
```{r}
library(caTools)
set.seed(123)
split <- sample.split(df$TravelInsurance, SplitRatio=0.80) 
df.train <- subset(df, split==TRUE)
df.test <- subset(df, split==FALSE)

head(df.train)
```

#Check for NA
```{r}
any(is.na(df.train))
any(is.na(df.test))
```

###Logistic Regression
```{r}
log_model1 <- glm(formula=TravelInsurance ~ . , family=binomial, data = df.train)

summary(log_model1)
```

#Improving the model with STEPAIC method
```{r}
library(MASS)

log_model2 <- stepAIC(log_model1, direction = "backward", trace = FALSE)

summary(log_model2)
```

Prediction
```{r}
log_pred <- predict(log_model2, df.test, type = 'response')
head(log_pred)
```

#AUC:0.768
```{r}
library(pROC)

roc(df.test$TravelInsurance, log_pred, plot=TRUE, print.auc=TRUE)
```

#Set threshold to define the outcome 1 or 0
```{r}
library(caret)

insurance.class<- ifelse(log_pred < 0.50, 0,1)
insurance.class <- as.factor(insurance.class)

table(insurance.class)
```


#Confussion Matrix
#Accuracy : 0.7481
```{r}
library(caret)
library(lattice)
confusionMatrix(df.test$TravelInsurance, insurance.class)
```


###Decision Tree 
```{r}
train_dt <- df.train
test_dt <- df.test

nrow(test_dt)
any(is.na(train_dt))
```

#Fitting data set to the Training set
```{r}
library(rpart)
tree<-rpart(formula = TravelInsurance ~., method = 'class', data = train_dt)
```

#Predicting the Test set results
```{r}
y_pred = predict(tree, newdata = test_dt[-9])
head(y_pred)
#Sum of each row equal to 1 
```

#Set threshold to 0.5.  < 0.5 =class 1 / > 0.5 =class 0
```{r}
y_pred_class = ifelse(y_pred[,'0']>=0.5, 0,1)
head(y_pred_class)
```

#Visualize the model
```{r}
library(rpart.plot)
prp(tree)
```

#AUC: 0.782
```{r}
library(pROC)
result.roc = roc(test_dt$TravelInsurance, y_pred[, '0'])
plot(result.roc, print.auc=TRUE)
```

#Confusion matrix 
#Accuracy : 0.8413
```{r}
y_pred_class_fac = as.factor(y_pred_class)

confusionMatrix(test_dt$TravelInsurance, y_pred_class_fac)
```


###Random Forest 

#Re-assign train and test set
```{r}
train_rf<-df.train
test_rf<-df.test

str(train_rf)
```

#Build random forest model
```{r}
library(randomForest)

rf_model <- randomForest(formula =TravelInsurance ~ ., method='class',
                 data = train_rf)
rf_model
```

#Check importance of every variable
#Anuual income, Age, and Family Member are the top 3 variables that show inportance to the outcome variable
```{r}
importance(rf_model)
```

# Predicting the Test set results
```{r}
rf_result = predict(rf_model, newdata = test_rf)

head(rf_result)
```

#Get probability to calculate for AUC
```{r}
probability = predict(rf_model, newdata = test_rf,type="prob")

head(probability)
```

#AUC: 0.807
```{r}
result.roc = roc(test_rf$TravelInsurance, probability[, '1'])

plot(result.roc, print.auc=TRUE)
```


#Confussion matrix
#Accuracy : 0.8413
```{r}
confusionMatrix(test_rf$TravelInsurance, rf_result)
```


###Comapre the models 

```{r}
lapply(list(log_model2, rf_model),FUN = AIC)
```





###Conclusion 






















